Cluster Difference Imaging Photometric Survey (CDIPS) II: A Jupiter-Sized Planet Candidate in IC~2602

### 2020-06-09 paper/ms.tex
minor paper updates

\subsubsection{Archival Imaging}
    Archival SERC-J and AAO-SES plates are available for the \tn\
field\footnote{\url{https://archive.stsci.edu/cgi-bin/dss_form}}.
These plates were acquired in 1982 and 1992, respectively.
For high proper motion stars archival imagery can be used to
detect slowly moving background stars that might be an
astrophysical false-positive source
({\it e.g.}, \citealt{huang_pimen_2018}).
However \tn\ has only moved $\approx0.7''$ between 1982 and
present, in comparison to the $\approx2.0''$ FWHM of the target on
the plates.
We therefore cannot resolve it with great confidence from
background sources not already resolved through more modern
imaging.

>>>>

\subsubsection{Patient Imaging}
    Archival SERC-J and AAO-SES plates are available for the \tn\
field\footnote{\url{https://archive.stsci.edu/cgi-bin/dss_form}}.
These plates were acquired in 1982 and 1992, respectively.
For high proper motion stars archival imagery can be used to
detect slowly moving background stars that might be an
astrophysical false-positive source
({\it e.g.}, \citealt{huang_pimen_2018}, CITE VANDERBURG 19).
However \tn\ has only moved $\approx0.7''$ between 1982 and
present, in comparison to the $\approx2.0''$ FWHM of the target on
the plates.
We therefore cannot resolve it with great confidence from
background sources not already resolved through more modern
imaging.
